### 2014-06-29 patchy-selection-paper.tex
notes on lit

>>>>

\section{Notes: for intro/discussion}

- leimu2008metaanalysis: local adaptation not ubiquitous but common; mostly in large population sizes.
- robertson1960theory: dependence of Ne on the degree of adaptation
- lots of local adaptation stuff on plants and conservation genetics; ties into plasticity and range limits.
- but also: Neurospora (ellison2011) and salmonids (fraser2011)
- swamping in Mayr 1963, Animal Species and Evolution?
- hanson1966effects: original observation of minimum patch size, in simulation?
- macnair1991: larger effects more common in e.g. heavy metal sites
- schat1996: silene parallel adaptation to mine tailings
- kaweki: a review.
- fourneir-level2011: map of arabidopsis local adaptation
- reviews for local adapt in marine (sanford2011), trees (savolainen2007)
